Thoughts on resubmission within ARC1

### 2009-03-13 doc/client/client_technical.tex
spelling corrections

This document describes from a technical viewpoint a plugin based
client library for the new Web Service (WS) based Advanced Resource
Connector~\cite{arc} (ARC) middleware. The library consists of a set
of C++ classes for

\begin{itemize}
\item{handling proxy, user and host certificates,}
\item{performing resource discovery and information retrieval,}
\item{filtering and brokering of found resources,}
\item{job submission and management and}
\item{data handling.}
\end{itemize}

All capabilities are enabled for three different grid flavours
(Production ARC, ARC1 and gLite~\cite{glite}) through a modular design
using plugins specialized for each supported middleware. Future
extensions to support additional middlewares involve plugin
compilation only i.e.\ no recompilation of main libraries or clients
is necessary.

@@

In the following we will give a functionality overview in
Section~\ref{sec:FuncOver} while all technical details will be given
in Section~\ref{sec:Implementation}. Section~\ref{sec:cli} will
through examples show how command line interfaces can be built upon
the library.

@@

\begin{enumerate}
\item{The {\TargetGenerator} takes three arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second and third arguments contain lists of strings. The first list
  contains individually selected and rejected computing services,
  while the second list contains individually selected and rejected
  index servers. Rejected servers and services are identified by that
  its name is prefixed by a minus sign in the lists. The name of the
  servers and services should be given either in the form of an alias
  defined in the {\UserConfig} object or as the name of its grid
  flavour followed by a colon and the URL of its information contact
  endpoint.}
\item{These lists are parsed through alias resolution before being
  used to initialize the complete list of selected and rejected
  {\URL}s pointing to computing services and index servers.}
\item{For each selected index server and computing service a
  {\TargetRetriever} plugin for the server's or service's grid flavour
  is loaded using the ARC loader. The {\TargetRetriever} is
  initialized with its {\URL} and the information about whether it
  represents a computing service or an index server.}
\item{An external call is received calling for targets to be
  prepared. The call for targets is processed by each
  {\TargetRetriever} in parallel.}
\item{A {\TargetRetriever} representing an index server first tries to
  register at the index server store kept by the {\TargetGenerator}.
  If allowed to register, the index server is queried and the query
  result processed. The {\TargetGenerator} will not allow
  registrations from index servers present in its list of rejected
  index servers or from servers that have already registered
  once. Index servers often register at more than one index server,
  thus different {\TargetRetriever}s may discover the same server.}
\item{If while processing the query result the {\TargetRetriever}
  finds an other registered index server or a registered computing
  service it creates a new {\TargetRetriever} for the found server or
  service and forwards the call for targets to the new
  {\TargetRetriever}.}
\item{A {\TargetGenerator} representing a computing service first
  tries to register at the service store kept by the
  {\TargetGenerator}. If allowed to register, the computing server is
  queried and the query result processed. The {\TargetGenerator} will
  not allow registrations from computing services present in its list
  of rejected computing services or from service that have already
  registered once. Computing services often register at more than one
  index server, thus different {\TargetRetriever}s may discover the
  same service.}
\item{When processing the query result the {\TargetRetriever} will
  create an {\ExecutionTarget} for each queue found on the computing
  service and collect all possible information about them. It will
  then store the {\ExecutionTarget} in the found targets store kept
  by the {\TargetGenerator} for later usage (e.g.\ status printing or
  job submission).}
\end{enumerate}

@@

Job submission starts with the resource discovery and target
preparation as outlined in the Section~\ref{sec:TargetDiscovery}. Not
until a list of possible targets (which allows the user) is available
is the job description read in order to enable bulk job submission of
widely different jobs without having to reperform the resource
discovery. In addition to the classes mentioned above the job
submission makes use of the {\Broker}, {\JobDescription} and
{\Submitter} classes.  The {\Submitter} is base class for further grid
middleware specific specialization (plugin) similarly to the {\TargetRetriever}.

@@

Once a job is submitted job related information (job identification
string, cluster etc.) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

The {\TargetRetriever} is base class for {\TargetRetriever} grid
middleware specializations and inherits from the {\ACC} base class in
order to be loadable by the ARC \texttt{Loader}. It is designed to
work in conjunction with the {\TargetGenerator} and contains the pure
virtual method

@@

Following a broker ranking jobs are to be submitted. Since all
information about the selected computing service resides within the
selected {\ExecutionTarget}, the {\ExecutionTarget} is capable of
returning a {\Submitter} capable of submitting a job to the service it
represents.

@@

The {\UserConfig} object is used to configure the security related
information needed by the {\Submitter}.

@@

The {\texttt PreFilterTargets} method compares every hardware and software requirement given in the job description against the 
computing resource (cluster) specifications stored in the {\ExecutionTarget}. If the{\ExecutionTarget} doesn't fulfil 
the requirements imposed by the job description, or it is impossible to carry out the matchmaking due to incomplete information 
published by the computing resource, the {\ExecutionTarget} will be removed from the list of possible targets. A detailed overview 
of the matchmaking between {\JobDescription} and {\ExecutionTarget} attributes is given in Appendix~\ref{sec:broker-mapping}.

Once prefiltered the remaining {\ExecutionTarget}s should be ranked in order to return the ``best'' {\ExecutionTarget} for 
job submission. Different ranking methods are implemented by the specialized brokers, but for usability and consistency reasons 
these methods are encapsulated by the {\Broker} base class method

@@

The identification of the source description format is internally handled by a 
\texttt{JobDescriptionOrderer} class which identifies the format by pattern matching.
Once the format is determined from the elements are mapped from the original format (XRSL, JDL or JSDL) 
into the internal representation (the \texttt{JobInnerRepresentation} class). Mapping details 
are given in Section~\ref{sec:jobinnerrepresentation}.

@@

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} function as shown below:

@@

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data is available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these events the {\texttt GetProduct} 
method returns with a false and an empty product string. For limitations in the translation
see Section~\ref{sec:jobinnerrepresentation}.

@@

{\Submitter} is base class for grid specific specializations (plugin).
It submits job(s) to the service it represents and uploads (by the job
needed) local input files.

@@

The {\JobSupervisor} is responsible for loading the appropriate
{\JobController}s for managing jobs running on a certain grid
flavour. Job manipulation can be performed either on individual jobs
or on groups of jobs (e.g.\ all jobs running on certain cluster or all
jobs with job state ``FINISHED''), and in order to translate the
information given by the user into a set of loadable {\JobController}s
the {\JobSupervisor} makes extensive use of the local joblist file
housing information about all active jobs. Thus the {\JobSupervisor}
constructor becomes

@@

Although being loaded by the {\JobSupervisor} the {\JobController}
objects truly resides within the ARC {\Loader} which is a member of
the {\JobSupervisor} class. In order to get handles on the
{\JobController}s the inline method

@@

The {\JobController} is a base class for grid specific
specializations, but also the implementer of all public functionality
offered by the {\JobController}s. In other words all virtual functions
of the {\JobController} are private. The initialization of a
(specialized) {\JobController} object takes two steps. First the
{\JobController} specialization for the required grid flavour must be
loaded by the ARC {\Loader}, which sees to that the {\JobController}
receives information about its flavour (grid) and the local joblist
file containing information about all active jobs (flavour
independent). Next step is the filling of the {\JobController}'s job
pool \texttt{JobStore} which is the pool of jobs that the
{\JobController} can manage.

@@

\begin{enumerate}
\item{If the \texttt{jobids} list has entries, fill \texttt{JobStore}
  with the by user requested jobs.}
\item{If the \texttt{clusterselect} list has entries, fill
  \texttt{JobStore} with the jobs running on the selected clusters.}
\item{If clusters are rejected and \texttt{JobStore} has entries,
  remove from \texttt{JobStore} all jobs running on rejected
  clusters.}
\item{If \texttt{jobs} and \texttt{clusterselect} are both empty
  lists, fill \texttt{JobStore} with all jobs except those running on
  possible rejected clusters.}
\end{enumerate}

The steps above completes the initialization of the {\JobController}
which is now ready for handling jobs. The public functions of the
{\JobController} offer to get (download), clean, cancel, etc. one or
more jobs and uses the private specializations for issuing the
command. Here exemplified by the \texttt{Stat} command:

@@

The {\Job} is a generic job class for storing all job related
information. Attributes are derived from the Glue2 information model
and thus a mapping is needed for non Glue2 compliant grid middlewares.
Appendix~\ref{app:job} shows the present mapping schema.

All attributes of the {\Job} can be printed by the method

@@

The {\UserConfig} class handles the client setup i.e. proxy,
certificate and key location, user and system configuration and local
joblist location. Upon initialization (constructor) the {\UserConfig}
locates the user files

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install
    Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration
  from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system
  configuration not already listed in the user configuration to the
  latter.}
\end{enumerate}

@@

\begin{itemize}
\item{If the \texttt{\$X509\_USER\_PROXY} environment variable is set,
  use its value to define a \texttt{ProxyPath} tag in \texttt{cfg}. If
  the file does not exist or can't be read exit with an error.}
\item{Otherwise, if the \texttt{\$X509\_USER\_CERT} environment
  variable is set, use its value and the value of the
  \texttt{\$X509\_USER\_KEY} environment variable to define
  \texttt{CertificatePath} and \texttt{KeyPath} tags in \texttt{cfg}.
  If \texttt{\$X509\_USER\_KEY} is not set or either file does not
  exist or can't be read exit with an error.}
\item{Otherwise, if the merged user configuration tree (see
  \texttt{ConfTree} contains a \texttt{ProxyPath} tag, copy it to
  \texttt{cfg}. If the file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the merged user configuration tree contains a
  \texttt{CertificatePath} tag, copy it to \texttt{cfg} along with the
  accompanying \texttt{KeyPath} tag. If the \texttt{KeyPath} tag is
  undefined or either file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the file \texttt{/tmp/x509up\_u + userid} exists
  add a \texttt{ProxyPath} tag in \texttt{cfg} pointing to it.}
\item{Otherwise, add \texttt{CertificatePath} and \texttt{KeyPath}
  tags to \texttt{cfg} pointing to
  \texttt{\$HOME/.globus/usercert.pem} and
  \texttt{\$HOME/.globus/userkey.pem}, respectively. If either file
  does not exist exit with error.}
\item{If the \texttt{\$X509\_CERT\_DIR} environment variable is set,
  use its value to define a \texttt{CACertificatesDir} tag in
  \texttt{cfg}. If the directory does not exist, exit with an error.}
\item{Otherwise, if the user ID is not zero and the directory
  \texttt{\$HOME/.globus/certificates} exists add a
  \texttt{CACertificatesDir} tag in \texttt{cfg} pointing to it.}
\item{Otherwise, add a \texttt{CACertificatesDir} tag in \texttt{cfg}
  pointing to \texttt{/etc/grid-security/certificates}. If the
  directory does not exist, exit with an error.}
\end{itemize}

@@

The ARC 0.x local information system uses the {\GT}~\cite{globus} GRIS
with a purpose made ARC schema. The information index server used is the
{\GT} GIIS. Both these servers are using the LDAP~\cite{ldap}
protocol. The specialization of the {\TargetRetriever} class for ARC0
is implemented using the ARC LDAP Data Management Component (DMC) (see
\cite{hed} for technical details).

@@

A-Rex implements the BES~\cite{ogsa-bes} standard interface. Since
this is a SOAP~\cite{soap} based interface the specializations of the
{\TargetRetriever}, {\Submitter} and {\JobController} classes make use
of a chain of ARC Message Chain Components (MCC~\cite{hed}) ending
with the SOAP client MCC.

The A-Rex service uses the https protocol put and get methods for
stage-in and stage-out of input and output files. Therefore, the ARC1
plugins requires the http DMC.

@@

\begin{itemize}
\item CREAM2 has a Web Service interface that fits the Web Service
  based ARC.
\item CREAM2 enables direct access to the gLite computing element
  without having to go via the gLite workload management system.
\item CREAM2 contains numerous improvements when compared to the
  earlier CREAM versions.
\item CREAM2 supports direct job status queries.
\item CREAM2 offers a convenient way of handling input and output
  files through accessing the input and output sandbox via GridFTP.
\end{itemize}

@@

CREAM has its own SOAP based interface. The CREAM
specializations of the {\Submitter} and {\JobController} classes
therefore use an MCC chain ending with the SOAP client MCC the same 
way the ARC1 plugin does.

@@

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked top.}
\item{If more than one {\ExecutionTarget} has zero queue the targets are randomly reshuffled based upon how many free slots 
they have. E.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% probability of becoming the top ranked cluster.}
\end{enumerate}

@@

The {\DataBroker} ranks the {\ExecutionTarget}s according to how many megabytes of the requested input files that already 
stored in the cache of the computing resource the {\ExecutionTarget} represents. The broker is motivated by that jobs should 
be submitted to {\ExecutionTarget}s where the data already is, thus reducing the network load on both the computing resource 
and client side. The ranking method is based upon the A-REX\footnote{http://www.knowarc.eu/download/D1.2-3\_documentation.pdf} 
interface {\texttt CacheCheck} for querying for the presence of the file in the cache directory. This interface has a limitation 
in the current implementation as it can only use cache directory of format

\begin{shaded}
\begin{verbatim}
cachedir="/tmp/cache"
\end{verbatim}
\end{shaded}

If the cachedir parameter involves {\%}U or other substitute element then the {\texttt CacheCheck} will not work.

@@

\begin{enumerate}
\item{Only the A-REX service has {\texttt CacheCheck} method, thus {\ExecutionTarget}s not running A-REX are removed.
therefore the other clusters will be ignored.}
\item{Information about input files is collected from the JobInnerRepresentation.}
\item{Each {\ExecutionTarget} is queried (through the {\texttt CacheCheck} method) for the existence of input files. 
A single query is used for achieving all the necessary information and file sizes are summarized. If there is problems 
determining file sizes, then the summarized size will be zero.}
\item{The possible {\ExecutionTarget}s are ranked in a descending order according to the amount of input data they have in cache.}
\end{enumerate}

@@

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status
  queries.}
\item{\texttt{arcsub} - for grid job submission}
\item{\texttt{arcget} - for downloading output of finished, cancelled
  or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory
  including all contents}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a
  running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's
  local XML file about active jobs.}
\item{\texttt{arcresub} - for redoing an entire job on the same or a new
  computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from an ARC1 
  computing resource to another.}
\end{enumerate}

>>>>

This document describes from a technical viewpoint a plugin-based
client library for the new Web Service (WS) based Advanced Resource
Connector~\cite{arc} (ARC) middleware. The library consists of a set
of C++ classes for

\begin{itemize}
\item{handling proxy, user and host certificates,}
\item{performing computing resource discovery and information retrieval,}
\item{filtering and brokering of found computing resources,}
\item{job submission and management and}
\item{data handling.}
\end{itemize}

All capabilities are enabled for three different grid flavours
(Production ARC, ARC1 and gLite~\cite{glite}) through a modular design
using plugins specialized for each supported middleware. Future
extensions to support additional middlewares involve plugin
compilation only i.e., no recompilation of main libraries or clients
is necessary.

@@

In the following we will give a functionality overview in
Section~\ref{sec:FuncOver} while all technical details will be given
in Section~\ref{sec:Implementation}. Section~\ref{sec:cli} will
show through examples how command line interfaces can be built upon
the library.

@@

\begin{enumerate}
\item{The {\TargetGenerator} takes three arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second and third arguments contain lists of strings. The first list
  contains individually selected and rejected computing services,
  while the second list contains individually selected and rejected
  index servers. Rejected servers and services are identified by that
  its name is prefixed by a minus sign in the lists. The name of the
  servers and services should be given either in the form of an alias
  defined in the {\UserConfig} object or as the name of its grid
  flavour followed by a colon and the URL of its information contact
  endpoint.}
\item{These lists are parsed through alias resolution before being
  used to initialize the complete list of selected and rejected
  {\URL}s pointing to computing services and index servers.}
\item{For each selected index server and computing service a
  {\TargetRetriever} plugin for the server's or service's grid flavour
  is loaded using the ARC loader. The {\TargetRetriever} is
  initialized with its {\URL} and the information about whether it
  represents a computing service or an index server.}
\item{An external call is received calling for targets to be
  prepared. The call for targets is processed by each
  {\TargetRetriever} in parallel.}
\item{A {\TargetRetriever} representing an index server first tries to
  register at the index server store kept by the {\TargetGenerator}.
  If allowed to register, the index server is queried and the query
  result processed. The {\TargetGenerator} will not allow
  registrations from index servers present in its list of rejected
  index servers or from servers that have already registered
  once. Index servers often register at more than one index server,
  thus different {\TargetRetriever}s may discover the same server.}
\item{If while processing the query result the {\TargetRetriever}
  finds another registered index server or a registered computing
  service it creates a new {\TargetRetriever} for the found server or
  service and forwards the call for targets to the new
  {\TargetRetriever}.}
\item{A {\TargetGenerator} representing a computing service first
  tries to register at the service store kept by the
  {\TargetGenerator}. If allowed to register, the computing server is
  queried and the query result processed. The {\TargetGenerator} will
  not allow registrations from computing services present in its list
  of rejected computing services or from service that have already
  registered once. Computing services often register at more than one
  index server, thus different {\TargetRetriever}s may discover the
  same service.}
\item{When processing the query result the {\TargetRetriever} will
  create an {\ExecutionTarget} for each queue found on the computing
  service and collect all possible information about them. It will
  then store the {\ExecutionTarget} in the found targets store kept
  by the {\TargetGenerator} for later usage (e.g.\ status printing or
  job submission).}
\end{enumerate}

@@

Job submission starts with the resource discovery and target
preparation as outlined in the Section~\ref{sec:TargetDiscovery}. Not
until a list of possible targets (which authorize the user) is available
is the job description read in order to enable bulk job submission of
widely different jobs without having to reperform the resource
discovery. In addition to the classes mentioned above the job
submission makes use of the {\Broker}, {\JobDescription} and
{\Submitter} classes.  The {\Submitter} is base class for further grid
middleware specific specialization (plugin) similarly to the {\TargetRetriever}.

@@

Once a job is submitted, job related information (job identification
string, cluster etc.) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

The {\TargetRetriever} is the base class for grid middleware specialized 
{\TargetRetriever}s and inherits from the {\ACC} base class in
order to be loadable by the ARC \texttt{Loader}. It is designed to
work in conjunction with the {\TargetGenerator} and contains the pure
virtual method

@@

All information needed to submit a job is stored in the {\ExecutionTarget}, 
and the {\ExecutionTarget}'s method

@@

returns a {\Submitter} which is used to submit jobs. The {\UserConfig} object 
is used to configure the security related information needed by the {\Submitter}.

@@

The {\texttt PreFilterTargets} method compares every hardware and software requirement given in the job description against the 
computing resource (cluster) specifications stored in the {\ExecutionTarget}. If the{\ExecutionTarget} doesn't fulfil 
the requirements imposed by the job description, or it is impossible to carry out the matchmaking due to incomplete information 
published by the computing resource, the {\ExecutionTarget} will be removed from the list of possible targets. A detailed overview 
of the matchmaking between {\JobDescription} and {\ExecutionTarget} attributes is given in Appendix~\ref{app:broker-mapping}.

Once prefiltered, the remaining {\ExecutionTarget}s should be ranked in order to return the ``best'' {\ExecutionTarget} for 
job submission. Different ranking methods are implemented by the specialized brokers, but for usability and consistency reasons 
these methods are encapsulated by the {\Broker} base class method

@@

The setSource method takes a source job description string as input and identifies it's format 
(language) through pattern matching (the \texttt{JobDescriptionOrderer} class).
Once the format is known, the source elements are mapped from the original format (XRSL, JDL or JSDL) 
into an internal representation (the \texttt{JobInnerRepresentation} class). Mapping details 
are given in Section~\ref{app:jobinnerrepresentation}.

@@

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known, the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} function as shown below:

@@

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these cases the {\texttt GetProduct} 
method returns with a false value and an empty product string. For limitations in the translation
see Section~\ref{app:jobinnerrepresentation}.

@@

{\Submitter} is the base class for grid middleware specialized {\Submitter}s (plugins).
It submits job(s) to the service it represents and uploads (needed by the job) local 
input files.

@@

The {\JobSupervisor} is responsible for loading the appropriate
{\JobController}s for managing jobs running on a certain grid
flavour. Job manipulation can be performed either on individual jobs
or on groups of jobs (e.g.\ all jobs running on certain cluster or all
jobs with job state ``FINISHED''), and in order to translate the
information given by the user into a set of loadable {\JobController}s
the {\JobSupervisor} makes extensive use of the local joblist file
which house information about all active jobs. Thus the {\JobSupervisor}
constructor becomes

@@

Although loaded by the {\JobSupervisor} the {\JobController}
objects actually reside within the ARC {\Loader} which is a member of
the {\JobSupervisor} class. In order to get handles on the
{\JobController}s, the inline method

@@

The {\JobController} is a base class for grid specific
specializations, but also the implementer of all public functionality
offered by the {\JobController}s. In other words all virtual functions
of the {\JobController} are private. The initialization of a
(specialized) {\JobController} object takes two steps. First the
{\JobController} specialization for the required grid flavour must be
loaded by the ARC {\Loader}, which sees to that the {\JobController}
receives information about its flavour (grid) and the local joblist
file containing information about all active jobs (flavour
independent). The next step is the filling of the {\JobController}'s job
pool \texttt{JobStore} which is the pool of jobs that the
{\JobController} can manage.

@@

\begin{enumerate}
\item{If the \texttt{jobids} list has entries, fill \texttt{JobStore}
  with the jobs requested by the user.}
\item{If the \texttt{clusterselect} list has entries, fill
  \texttt{JobStore} with the jobs running on the selected clusters.}
\item{If clusters are rejected and \texttt{JobStore} has entries,
  remove from \texttt{JobStore} all jobs running on rejected
  clusters.}
\item{If \texttt{jobids} and \texttt{clusterselect} are both empty
  lists, fill \texttt{JobStore} with all jobs except those running on
  rejected clusters if there are any.}
\end{enumerate}

The steps above complete the initialization of the {\JobController}
which is now ready for handling jobs. The public functions of the
{\JobController} offer to get (download), clean, cancel, etc. one or
more jobs and use the virutal methods implemented by the grid middleware 
specialized {\JobController}s for issuing the command. Here exemplified 
by the \texttt{Stat} command:

@@

The {\Job} is a generic job class for storing all job related
information. Attributes are derived from the Glue2 information model
and thus a mapping is needed for non Glue2 compliant grid middlewares.

All attributes of the {\Job} can be printed by the method (longlist = true 
will give more details (long listing))

@@

The {\UserConfig} class handles the client setup i.e. proxy,
certificate and key location, user and system configuration and local
joblist location. Upon initialization (constructor) the {\UserConfig}
locates and reads the user files

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install
    Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration
  from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system
  configuration not already listed in the user configuration items to the
  latter.}
\end{enumerate}

@@

\begin{itemize}
\item{If the \texttt{\$X509\_USER\_PROXY} environment variable is set,
  use its value to define a \texttt{ProxyPath} tag in \texttt{ccfg}. If
  the file does not exist or can't be read exit with an error.}
\item{Otherwise, if the \texttt{\$X509\_USER\_CERT} environment
  variable is set, use its value and the value of the
  \texttt{\$X509\_USER\_KEY} environment variable to define
  \texttt{CertificatePath} and \texttt{KeyPath} tags in \texttt{ccfg}.
  If \texttt{\$X509\_USER\_KEY} is not set or either file does not
  exist or can't be read exit with an error.}
\item{Otherwise, if the merged user configuration tree (see
  \texttt{ConfTree}) contains a \texttt{ProxyPath} tag, copy it to
  \texttt{ccfg}. If the file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the merged user configuration tree contains a
  \texttt{CertificatePath} tag, copy it to \texttt{ccfg} along with the
  accompanying \texttt{KeyPath} tag. If the \texttt{KeyPath} tag is
  undefined or either file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the file \texttt{/tmp/x509up\_u + userid} exists
  add a \texttt{ProxyPath} tag in \texttt{ccfg} pointing to it.}
\item{Otherwise, add \texttt{CertificatePath} and \texttt{KeyPath}
  tags to \texttt{ccfg} pointing to
  \texttt{\$HOME/.globus/usercert.pem} and
  \texttt{\$HOME/.globus/userkey.pem}, respectively. If either file
  does not exist exit with error.}
\item{If the \texttt{\$X509\_CERT\_DIR} environment variable is set,
  use its value to define a \texttt{CACertificatesDir} tag in
  \texttt{ccfg}. If the directory does not exist, exit with an error.}
\item{Otherwise, if the user ID is not zero and the directory
  \texttt{\$HOME/.globus/certificates} exists add a
  \texttt{CACertificatesDir} tag in \texttt{ccfg} pointing to it.}
\item{Otherwise, add a \texttt{CACertificatesDir} tag in \texttt{ccfg}
  pointing to \texttt{/etc/grid-security/certificates}. If the
  directory does not exist, exit with an error.}
\end{itemize}

@@

The ARC 0.x local information system uses the {\GT}~\cite{globus} GRIS
with a custom made ARC schema. The information index server used is the
{\GT} GIIS. Both these servers use the LDAP~\cite{ldap}
protocol. The specialization of the {\TargetRetriever} class for ARC0
is implemented using the ARC LDAP Data Management Component (DMC) (see
\cite{hed} for technical details).

@@

A-Rex implements the BES~\cite{ogsa-bes} standard interface. Since
this is a SOAP-based~\cite{soap} interface, the specializations of the
{\TargetRetriever}, {\Submitter} and {\JobController} classes make use
of a chain of ARC Message Chain Components (MCC~\cite{hed}) ending
with the SOAP client MCC.

The A-Rex service uses the https protocol \texttt{put} and \texttt{get} methods for
stage-in and stage-out of input and output files. Therefore, the ARC1
plugins requires the http DMC.

@@

\begin{itemize}
\item CREAM2 has a Web Service interface that is very similar to the Web Service
  based ARC.
\item CREAM2 enables direct access to the gLite computing element
  without having to go via the gLite workload management system.
\item CREAM2 contains numerous improvements when compared to the
  earlier CREAM versions.
\item CREAM2 supports direct job status queries.
\item CREAM2 offers a convenient way of handling input and output
  files through accessing the input and output sandbox via GridFTP.
\end{itemize}

@@

CREAM has its own SOAP-based interface. The CREAM
specializations of the {\Submitter} and {\JobController} classes
therefore use an MCC chain ending with the SOAP client MCC the same 
way the ARC1 plugin does.

@@

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked first.}
\item{If more than one {\ExecutionTarget} has zero queue, the targets are randomly reshuffled based upon how many free slots 
they have, e.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% probability of becoming the top ranked cluster.}
\end{enumerate}

@@

The {\DataBroker} ranks the {\ExecutionTarget}s according to how many megabytes of the requested input files that already 
stored in the cache of the computing resource the {\ExecutionTarget} represents. The broker is motivated by that jobs should 
be submitted to {\ExecutionTarget}s where the data already is, thus reducing the network load on both the computing resource 
and client side. The ranking method is based upon the A-REX\footnote{http://www.knowarc.eu/download/D1.2-3\_documentation.pdf} 
interface {\texttt CacheCheck} for querying for the presence of the file in the cache directory. This interface has a limitation 
in the current implementation and does not support per user caches.

@@

\begin{enumerate}
\item{Only the A-REX service has {\texttt CacheCheck} method, thus {\ExecutionTarget}s not running A-REX are removed.}
\item{Information about input files requested in the job description is collected from the \texttt{JobInnerRepresentation.}}
\item{Each {\ExecutionTarget} is queried (through the {\texttt CacheCheck} method) for the existence of input files. 
A single query is used for achieving all the necessary information and file sizes are summarized. If there are problems 
determining file sizes, then the summarized size will be zero.}
\item{The possible {\ExecutionTarget}s are ranked in a descending order according to the amount of input data they have in their cache.}
\end{enumerate}

@@

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status
  queries.}
\item{\texttt{arcsub} - for grid job submission.}
\item{\texttt{arcget} - for downloading output of finished, cancelled
  or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory
  including all contents.}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a
  running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's
  local XML file about active jobs.}
\item{\texttt{arcresub} - for redoing an entire job on the same or a new
  computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from an ARC1 
  computing resource to another.}
\end{enumerate}
